### 2021-05-15 response.tex

\documentclass{article}
\bibliographystyle{plos2015}
\usepackage[utf8]{inputenc}
\usepackage{textgreek}
\usepackage[
  left=3cm,
  right=2cm,
  top=2.5cm,
  bottom=2cm,
]{geometry}
\usepackage{csquotes}
\usepackage{hyperref}
\usepackage[framemethod=TikZ]{mdframed}
\mdfsetup{
        frametitle={
        \tikz[baseline=(current bounding box.east),outer sep=0pt]%
        \node[anchor=east, rectangle, fill=gray!40]
        {\strut `` ''};},
        innertopmargin=0pt,
        linecolor=gray!40,
        linewidth=2pt,topline=true,
        frametitleaboveskip=\dimexpr-\ht\strutbox\relax
    }

\newcommand{\webprov}{\textit{WebProv}}
\newcommand{\bcat}{\textbeta-catenin}
\newcommand{\wnt}{Wnt}
\newcommand{\provnode}{Provenance Node}
\newcommand{\provnodes}{Provenance Nodes}
\newcommand{\lee}{Lee et al. (2003)}
\newcommand{\RQ}{Research Question}
\newcommand{\A}{Assumption}
\newcommand{\As}{Assumptions}
\newcommand{\R}{Requirement}
\newcommand{\Rs}{Requirements}
\newcommand{\QM}{Qualitative Model}
\newcommand{\QMs}{Qualitative Models}
\newcommand{\SM}{Simulation Model}
\newcommand{\SMs}{Simulation Models}
\newcommand{\SE}{Simulation Experiment}
\newcommand{\SEs}{Simulation Experiments}
\newcommand{\SD}{Simulation Data}
\newcommand{\WD}{Wet-lab Data}
\newcommand{\WE}{Wet-lab Experiment}
\newcommand{\BSM}{Building Simulation Model}
\newcommand{\CSM}{Calibrating Simulation Model}
\newcommand{\VSM}{Validating Simulation Model}
\newcommand{\ASM}{Analyzing Simulation Model}

\title{Review response: \enquote{Relating simulation studies by provenance---Developing a family of Wnt signaling models}}
\author{Kai Budde, Jacob Smith, Pia Wilsdorf, Fiete Haack, Adelinde M. Uhrmacher}
\date{\today}

\begin{document}

\maketitle

\noindent Dear Prof. Pedro Mendes,\\
Dear Prof. Jason Haugh,\\
Dear Prof. Chris J. Myers,\\
Dear anonymous reviewer,\\
Dear Dr. David P. Nickerson,\\

\noindent we would like to thank all of you for your thorough and constructive feedback!

\section*{1\textsuperscript{st} Reviewer}

\begin{mdframed}
Much has been made recently of the importance of reproducibility of scientific research.
In biological simulation studies, such as this paper considers, this means providing the models and the analysis instructions in standard machine readable forms.
This paper takes this a step further to look at the issue of provenance for these models.
Namely, how are models related to previous models and experimental studies.
In particular, the authors looks at a family of 19 models of the Wnt signaling pathway, which that manually link together using the PROV-DM ontology.
To construct these relationships, they have developed a web tool, WebProv, to link studies with PROV-DM types and relations.
As the authors point out, extracting these relationships from published studies is a highly laborious process that requires many assumptions along the way.
Ideally, in the future, these provenance networks should be developed at the time of model construction during the simulation study.

This paper is an important demonstration of both the process of creating and utility of provenance networks for simulation studies.
The prototype software tool presented should help facilitate future such activities.
This proof-of-concept presented in this paper should become a tutorial for others that would undertaken this task for their models and simulation studies.
The key issue remaining is how to motivate and facilitate others to create this information.
This is not a problem that the authors can solve, but rather one that the community and the journal publishers should devote time and energy to in order to further improve the reproducibility of science.
\end{mdframed}

Thank you, Prof. Myers. We agree with you and appreciate your kind feedback on the importance of our work.

\section*{2\textsuperscript{nd} Reviewer}
\begin{mdframed}
This is an interesting paper that looks in detail at 19 Wnt related modeling papers.
As a practicing modeler myself the most interesting pages started on page 14 (Provenance of individual Wnt simulation models) which discusses the various issues encountered, problems with the current ontolgies etc.
I think this is the most important part of the paper from the point of view of the plos comp bio readership, such analyses have not been done as exhaustively as this one.

Some of the material, particular the descriptions of the provenance entries (which seems to dominate the paper) could be summarized in a table and the textual component moved to an appendix. This would allow the reader to get straight to the most interesting papers of the paper. \ldots
\end{mdframed}

Thank you, dear reviewer, for finding our work interesting!
We agree with you that some readers might find the second part of the \textit{Results and discussion} section more interesting than the first part.
The first part of the section, entitled \enquote{Further steps towards a PROV-DM ontology for cellular biochemical simulation models}, contains our definitions and examples of every entity and activity type used in our provenance data model.
It belongs to the knowledge engineering part of our contribution, which is a prerequisite for the detailed provenance information of the Wnt models.
We have extended the introductory paragraph of the \textit{Results and discussion} section.
This should make it clearer to the reader that the first part may be skipped by those who wish to jump directly to the Wnt model family.
The changes are in lines 172--176(???).
%TODO check line numbers

\begin{mdframed}
\ldots\,Caption: The captions to some of the figures could be improved.

Fig 2: This caption starts with the word ‘additionally’ which doesn’t sit well.
Also the caption is too short, given that this is probably one of the more important figures.
It took me a while to realize what the terms ASM, CSM etc meant (They were in Table 2).
I would spell out these abbreviations (ASM, CSM, VSM, BSM) in the caption (Table 2 can remain unchanged), this will save the reader for having to search for their meaning.
The caption would also add one sentence on how to read the figure.
I know that earlier on the authors explain what an arrow means but that was some pages away and since plos comp bio are generally no computer scientists I would add that explanation of the arrow to the caption as well.

Fig 3: In general, notation used in UML diagrams is not familiar to most modelers but in this case the diagram looks simple enough that its seems fairly self-explanatory. No action required. \ldots
\end{mdframed}

We have adapted and extended the caption of Fig 2 and added the abbreviations (BSM, QM, \dots) to the legend of the figure (instead of the caption).
We hope that this makes the content of the figure clearer to the reader.

\begin{mdframed}
\ldots\,Minor: Typo in caption first sentence : ‘prociding’, I’m not sure what that word means, probably a typo but not sure what word should be there instead? \ldots
\end{mdframed}

Thanks for pointing out the typo.
We have fixed it.

\begin{mdframed}
\ldots\,Software: As it stands it is likely that very few people will use WebProv, the reason is that it requires far too much work to install, plus does it also require a backend sever?

The tool looks useful so why make it difficult to get hold of?

What I would recommend is move everything if possible to the client (including the database which doesn’t seem large) and host it as a github web page project so that when a user clicks on the url the application will show up, no installation necessary (which I think is one of the main attractions of web software) – see https://pages.github.com/. I strongly recommend something like this otherwise your work will not have the impact it should. \ldots
\end{mdframed}

\textbf{TODO: Please add some sentences, Jacob. Thanks!}
Why GitHub Pages are not working anymore.
We are currently deploying WebProv on commercial servers which should make it easier for the readers of the publication to get an impression of the tool and the provenance information of the Wnt models.
It can be accessed here...
Due to funding restriction, we plan to shutdown this service by the end of the year.
It should still be relatively feasible to locally install the use the app by following the ReadMe (see next paragraph).

\begin{mdframed}
\ldots\,Documentation: There is no easily accessible documentation for the software. It looks like users are expected to download the github repo then select the indexl.html file in Docs. It would be better to host a proper (eg readthedocs) documentation on the github account itself. The only documentation link in the readme take a user to process manger 2 page. \ldots
\end{mdframed}

The documentation (usage and deployment) is available in the \href{https://github.com/SFB-ELAINE/WebProv#readme}{Readme on GitHub}.
We have adopted it to make is more comprehensible.
The \texttt{docs/} folder and \texttt{docs/index.html} file are removed.
It was used for the initial version of the application that could be deployed using GitHub Pages.

\begin{mdframed}
\ldots\,Minor:
1. Introduction, second paragraph, first sentence, ‘conduction’, is that the right word? \ldots
\end{mdframed}

We have changed the wording.

\begin{mdframed}
\ldots\, 2. There is no reference to the youtube video on page 4 (footnote 2), also put the github ural there as well since the github repository is mentioned.
\end{mdframed}

For most URLs, we have used hyperlinks.
Thus, clicking on \href{https://youtu.be/UzwHtptkYOU}{YouTube} in the former footnote 2 should have led you to the website \url{https://youtu.be/UzwHtptkYOU}.
We will make this video publicly available as it is if and only if the manuscript has been accepted for publication in PLOS Computation Biology.

Furthermore, we have also removed all footnotes and moved the information into the main text as required by PLOS Computational Biology.

\section*{3\textsuperscript{rd} Reviewer}

\begin{mdframed}
In this manuscript, the authors present a continuation of previous work to make use of the PROV-DM to represent provenance of biosimulation studies.
The authors then use this data model to encode the provenance of a number of Wnt signalling models from the literature, and use the encoded provenance knowledge to examine the relationships between these published studies.
The authors have also developed an open-source web-based tool providing a graphical user interface for creating, editing, exploring, and searching the provenance knowledge encoded in this manner.
This seems to be a very useful approach for capturing provenance knowledge of systems biology modelling studies and appears to be extensible to capture richer provenance semantics as the collection/recording methods improve in future and this approach is applied in different domains or different types of models.

The authors should be commended for making all the software and data used in this manuscript freely available and documented in a manner sufficient to enable others to repeat the analysis presented here. \ldots
\end{mdframed}

Thank you, Dr. Nickerson!
We are striving to publish all material related to our research and the publication.

\begin{mdframed}
\ldots\, I suggest the entire manuscript is thoroughly proof-read as some of the grammar and word choices are a bit unusual. "cell biological systems" in the abstract is one example that could be tidied up. \ldots
\end{mdframed}

We have proofread the manuscript and corrected all mistakes.
We hope all language problems have been eliminated.
%TODO Let Jacob re-read everything before submitting it.

\begin{mdframed}
\ldots\, As the authors state, the knowledge they have extracted from the literature and encoded in the example provenance graph used in this work makes a useful contribution to the community of potential users of these Wnt signally models.
I wonder if the authors have any plans or thoughts on the integration of this knowledge into a community repository, perhaps in a way that others could contribute to?
For the subset of models that are available in the Biomodels database, for example, could the provenance knowledge be contributed back to the database? \ldots
\end{mdframed}

As we have stated in our conclusion, we think that accessible provenance information would be a valuable extension of the BioModels (or any other simulation model) repository.
Right now, comparing the entries of BioModels to our approach, the database contains provenance (meta-)information of type Simulation Model and may, additionally, contain information of type Simulation Experiment and Simulation Data.
The latter two usually comprise an experiment specification file, for instance a SED-ML file, as well as a figure showing the simulated data.
In our case, the following BioModels entries contain information about the simulation experiments: the entry for Lee et al. (2003)~\cite{Lee2003} contains both a SED-ML (and COPASI) file to reproduce parts of Fig 6 of that publication (corresponding to our SD6) and the entry for Padala et al. (2017)~\cite{Padala2017}contains the COPASI file to reproduce Fig 2A-C of that publication (corresponding to our SD3).
The overview of a model entry might also include information about Research Questions and Assumptions.
The other entities/activities and, more importantly, most relations are not available.

Other researchers have looked at updates of a model in a repository using BiVeS, an \enquote{algorithm to detect and communicate the differences in computational models describing biological systems}~\cite{Scharm2016a} and COMODI, \enquote{an ontology to characterise differences in versions of computational models in biology}~\cite{Scharm2016}.
Scharm et al. (2018) have also asked the maintainers of model repositories to add the possibility of entering provenance information~\cite{Scharm2018}: \enquote{We want to encourage the maintainers of repositories to provide a system where curators and modellers can transparently track the evolution of a project, e.g. using PROV-O [24] to encode the provenance and COMODI to describe reason, intention, and effects of a change.}

We are planning to contact the BioModels team and would be happy to see (some of) the provenance data acquired added to the repository.
However, all of this should be a community effort, which needs a broader discussion beforehand.

\begin{mdframed}
\ldots\, Following that thought, some of the provenance knowledge captured here is similar to that represented in the Biomodels database using the "isDerivedFrom" predicate in the SBML model annotations (see for example the analysis of diabetes models presented in \url{https://dx.doi.org/10.1038\%2Fpsp.2013.30}).
Have the authors compared this knowledge for the subset of Wnt models available in the Biomodels database to see if similar (although less semantically rich) patterns of model evolution are present to their analysis presented in this manuscript? \ldots
\end{mdframed}

Thank you for pointing out the publication by Ajmera et al. (2013).
A key finding of the review is the following: \enquote{The model relationship map (Figure 3) provides a complete overview of the evolution of most diabetes models available in the literature to-date and highlights the significance of sharing and reuse of models.}

For some models presented in Figure 3, this relationship is also shown in BioModels using the qualifier \href{http://biomodels.net/model-qualifiers/isDerivedFrom}{\textit{isDerivedFrom}}: \enquote{The modelling object represented by the model element is derived from the modelling object represented by the referenced resource (modelling object B).
This relation may be used, for instance, to express a refinement or adaptation in usage for a previously described modelling component}.

When comparing this qualifier with our approach, we find that whenever we have a connection of the kind `Building Simulation Model (of simulation study \textit{i}) $\longrightarrow$ Simulation Model (of simulation study \textit{j})', we could add `model \textit{i} \textit{isDerivedFrom} model \textit{j}' to BioModels (see Figure~\ref{fig:KimDerived}).

As we have stated in our manuscript, \enquote{we have (...) not included the direct connection between two activities or two entities, such as the possibility to have a model being derived from another model. Thus, we have not included (...)  \texttt{WasDerivedFrom}, which describes a direct transformation (update) of an entity into a new one}.

Out of six Wnt models included in BioModels, two comprise information about model relations.
First, the model by Kim et al. (2007) has \textit{isDerivedFrom} information: `DOI 10.1007/3-540-36481-1\_11' (Cho et al. 2003) and `PubMed 1455190' (Lee et al. (2003)).
When comparing it with our provenance information, we have found an \textit{isDerivedFrom}-equivalent connection to Cho et al. (2003) and Cho et al. (2006).
The latter is missing in BioModels.
Cho et al. (2006), on the other hand, is connected to Lee et al. (2003).
(See our \href{https://github.com/SFB-ELAINE/SI_Provenance_Wnt_Family/tree/main/ProvenanceInformation}{GitHub repository} with additional files.
This link has also been given in the main text.)

Second, the model by Padala et al. (2017) contains the following \textit{isDerivedFrom} information: `BIOMD0000000623' (Orton et al. (2009)), `BIOMD0000000033' (Brown et al. (2004)), and `BIOMD0000000149' (Kim et al. (2007)).
All of these connections are also contained in our provenance graph.

We will provide the BioModels team with further \textit{isDerivedFrom}-information that could be added to the annotations of the Wnt models in the repository.
This information is extracted from our provenance graph by querying for a \BSM{} activity (of simulation study \textit{i}) that \textit{used} a \SM{} entity (of another simulation study \textit{j}).

\begin{figure}[!h]%figure
\centering
\includegraphics[width=0.9\textwidth]{Provenance_2007_Kim_derivedFromExample}
\caption{{\bf Provenance graph of the study by Kim et al. (2007)~\cite{Kim2007}.}
Additionally, the three entities and their corresponding relations (SM1(Cho2003) $\leftarrow$ BSM1(Kim2007) $\leftarrow$ SM1(Kim2007)) are surrounded by a green triangle showing the possibility to extract \textit{isDerivedFrom} information from provenance graphs.}
\label{fig:KimDerived}
\end{figure}

%However, it is unclear to us how their relationship map has been generated.
%We have also checked the status \textit{isDerivedFrom} in BioModels for all models that are present in BioModels and that %are directly connected in Figure 3 of their publication (\enquote{models that are derived from another model, by adopting some mathematical feature(s) or hypothesis}).
%We have found that all connected models but one that include \textit{isDerivedFrom} information share at least one author.
%The only exception is the model by Nyman 2011.
%Some models that are connected to the Nyman 2011 model do not share authors.
%In Figure 3, instead of Koschorreck 2008, Kiselyov 2009 should be connected to Nyman 2011, as it is stated in \href{https://www.ebi.ac.uk/biomodels/BIOMD0000000356}{BioModels}.

%\begin{itemize}
%\item Sturis 1991 (BIOMD0000000382) $\rightarrow$ Tolic 2000 (BIOMD0000000372): Tolic 2000 contains the information  \enquote{isDerivedFrom BIOMD0000000382}, but both publications share two authors: E. Mosekilde and J. Sturis.
%\item Bertram 1995 (BIOMD0000000374) $\rightarrow$ Mears 1997 (BIOMD0000000375) also contains \enquote{isDerivedFrom BIOMD0000000374}, both publications share three authors: D. Mears, R. Bertram, and A. Sherman
%\item Wanant 2000 (MODEL1201140005 and MODEL1201140006) $\rightarrow$ Sedaghat 2002 (BIOMD0000000137)  \enquote{isDerivedFrom PubMed 1890848, PubMed 1890850, BioModels Database MODEL1201140005, PubMed 8304439, BioModels Database MODEL1201140006}, but both publications share one author: M.J. Quon.
%\item Quon 1991a (60) $\rightarrow$ Sedaghat 2002 (65) $\rightarrow$ share at least one author
%\item Koschorreck 2008 (61) $\rightarrow$ Nyman 2011 (68) $\rightarrow$ arrow is mistakenly put from Koschorreck. It should connect Kiselyov 2009 (62) with Nyman 2011 (68) as looking at the models it has been derived from shows \url{https://www.ebi.ac.uk/biomodels/BIOMD0000000356}. $\rightarrow$some models to Nyman 2011 do not share authors.
%\item Brännmark 2010 (63) $\rightarrow$ Nyman 2011 (68) $\rightarrow$ share at least one author
%\end{itemize}

%Not in Biomodels (examples):
%Tiran 1975 (29) -> Sorensen 1985 (22) -> do not share any authors (Sorensen cites Tiran), but mentions that (part of) model has been used
%Bertram 2007 (S155) -> Chew 2009 (S156) -> do not share any authors, but mentions that (part of) the model has been used

### 2021-05-16 main.tex
first pass

%3) What is the methodology being used to answer the stated research question? (81 words)
Therefore, we exploit the provenance data model, PROV-DM, of the World Wide Web Consortium and, building on previous work, continue developing a PROV ontology for simulation studies.
Based on a case study of 19 \wnt{}/\bcat{} signaling models, we identify crucial entities and activities as well as useful metadata to both capture the provenance information of individual simulation studies and relate these forming a family of models.
The approach is implemented in \href{https://github.com/SFB-ELAINE/WebProv}{\webprov{}}, which allows one to insert and query provenance information.

%4) What are the results obtained? (73 words)
Our specialization of PROV-DM contains the entities \RQ{}, \A{}, \R{}, \QM{}, \SM{}, \SE{}, \SD{}, and \WD{} as well as activities referring to building, calibrating, validating, and analyzing a simulation model.
We show that most \wnt{} simulation models are connected to other \wnt{} models by using (parts of) these models.
However, the overlap, especially regarding the \WD{} used for calibration or validation of the models is small.

%5) What is the meaning and importance of these results? (52 words)
Making these aspects of developing a model explicit and queryable is an important step for assessing and reusing simulation models more effectively.
By this, it helps to integrate a new simulation model within a family of existing ones.
Our approach may lead to the development of more robust and valid simulation models.

%6) What are the directions for follow-up research?  (24 words)
We hope that it becomes part of a standardization effort and that modelers adopt the benefits of provenance when considering or creating simulation models.

@@

We revise a provenance ontology for simulation studies of cellular biochemical models.
Provenance information is useful for understanding the creation of a simulation model, because it does not only contain information about the entities and activities that have led to a simulation model but also the relations of these, which can be visualized.
It provides additional structure as research questions, assumptions, and requirements are singled out and explicitly related along with data, qualitative models, simulation models, and simulation experiments through a small set of predefined but extensible activities.

We have applied our concept to a family of 19 \wnt{} signaling models and implemented a web-based tool (\webprov{}) to store the provenance information of these studies.
The resulting provenance graph visualizes the story line within simulation studies and demonstrates the creation and calibration of simulation models, the successive attempts of validation and extension, and shows, beyond an individual simulation study, how the \wnt{} models are related.
Thereby, the steps and sources that contributed to a simulation model are made explicit.

@@

A plethora of work has emerged over the last two decades to support the execution and documentation of simulation studies (e.g., modeling and simulation life cycles~\cite{Balci2012}, workflows~\cite{Ruscheinski2019}, conceptual models~\cite{Wilsdorf2020b}).
Depending on the application domain, different modeling approaches have their own documentation guidelines~\cite{Monks2018, Erdemir2012, Grimm2010}.
In the case of systems biology, the \enquote{Minimum Information Requested in the Annotation of Biochemical Models (MIRIAM)}~\cite{LeNovere2005} and the \enquote{Minimum Information About a Simulation Experiment (MIASE)}~\cite{Waltemath2011} are two community standards used for documenting simulation models and corresponding simulation experiments.
A recent perspective by Porubsky et al. (2020)~\cite{Porubsky2020} looks at all stages of a biochemical simulation study and at tools supporting their reproducibility.
When looking at an entire simulation study and at the generation process of the included simulation model, these guidelines provide some indication about which information might be useful for documenting a complete simulation study as well as for establishing relationships between different simulation models.

% Why do we have more than one model for a specific system and how can we relate these models?
This is of particular interest when several simulation models for a system under consideration exist, offering different perspectives on the system, answering different questions, or reflecting the data and information available at the time of generation.
Model repositories such as BioModels~\cite{BioModels2020, BioModels2018}, JWS Online~\cite{Snoep2004}, or the CellML Model Repository~\cite{Lloyd2008} provide different means to retrieve and use simulation models.
% BioModels\footnote{\url{https://www.ebi.ac.uk/biomodels/}}, JWS Online\footnote{\url{https://jjj.biochem.sun.ac.za/}}, the CellML Model Repository\footnote{\url{https://models.cellml.org/}}
For example, querying the BioModels database for biochemical and cellular simulation models that contain proteins such as \wnt{}, Janus kinase (Jak), or mitogen-activated protein kinase (MAPK), which are associated with corresponding signaling pathways, returns for \wnt{} a set of 22 simulation models, for Jak a set of 12 simulation models and for MAPK a set of 139 simulation models (as of January 2021).
This already shows that MAPK is an intensively studied signaling pathway.
However, there is no way to easily compare these simulation models or to examine their relationships to each other.
Tools such as BiVeS~\cite{Scharm2016a} are helpful to compare different versions of one particular simulation model, but comparing different models---even of the same system---will be a difficult task because the syntax of these models (e.g., the names of the species), as well as reactions, might be completely different.
Instead of analyzing the similarities and differences in the specifications of simulation models to infer possible relationships between these simulation models, we will focus on context information, such as how a simulation model has been generated.

% How do models grow larger over time and what happens then?
Particularly, larger models are usually not built from scratch~\cite{Cvijovic2014}.
In general, simulation models are the outcome of extensive as well as interactive model and data generation activities that include, in addition to executing various simulation experiments and successive model refinements, the adaptation of already existing models, for example, by composition or extension~\cite{Peng2017, Peng2016, Cvijovic2014}.
Therefore, the complexity of a model grows over time as researchers add parts to the model or refine it.
Keeping track of these generation processes is the subject of provenance.

% What does provenance mean and tell us? How and where can we store this information?
Provenance provides \enquote{information about entities, activities, and people involved in producing a piece of data or thing, which can be used to form assessments about its quality, reliability or trustworthiness}~\cite{Belhajjame2013}.
Thus, it can be applied to many fields of science, art, and technology, including biochemical and cellular simulation models.
By exploiting standardized provenance data models, such as PROV-DM, this information is presented in a structured, queryable, and graphical form~\cite{Ruscheinski2018, Ruscheinski2017}.
In addition to providing crucial information about the generation of an individual simulation model and, thus, facilitating its reuse, provenance can be applied to reveal and exploit relationships between different simulation models.

% What is our goal of this publication? And what is the Wnt signaling pathway?
In this publication, we will identify and structure relevant information needed for the provenance of simulation studies and elucidate how a family of simulation models can be established through relating the models to each other.
As a case study, we will concentrate on 19 simulation studies of the \wnt{}/\bcat{} signaling pathway.
Among the different \wnt{} signaling pathways, the canonical \wnt{} or \wnt{}/\bcat{} signaling pathway is the most intensively studied one, \textit{in vitro}~\cite{MacDonald2009} as well as \textit{in silico}~\cite{Lloyd-Lewis2013}.
This pathway is considered to be one of the key pathways in development and regeneration, including cell fate, cell proliferation, cell migration and adult homeostasis~\cite{Steinhart2018, Giles2003}.
In deregulated forms, it is involved in human cancers and developmental disorders~\cite{Clevers2012, Logan2004}.

Our case study refers to the \wnt{}/\bcat{} signaling pathway only, which we call \wnt{} throughout the text.
We will present and use our web-based tool \webprov{} to store, present and query provenance information of these simulation studies.
Different queries and analyses of the family of 19 \wnt{} simulation models will then be used for finding further insights into the family of \wnt{} signaling simulation models.

@@

% General procedure of collecting provenance information
In order to gather all relevant information, the publications as well as the supporting materials---as they often contain model and experiment descriptions---were read thoroughly.
Referenced publications were checked, as well, whenever they appeared to be important for the development of the simulation model.
All information that resembled provenance entities were marked.
While reading a study, a first sketch of a possible provenance graph was being made.
Afterwards, a revision of all markings helped to finalize the graph and to remove duplicated entities.
Often, authors described their simulation study chronologically, which made it easy to determine the path of its development, but sometimes, the connections of the entities had to be inferred from the context.
In general, tracing the provenance of an entire simulation study in retrospective involved some interpretation of the results presented in the publication.

@@

The tool can be locally installed for testing and replicability purposes.
Details about its installation, as well as the code are found on \href{https://github.com/SFB-ELAINE/WebProv}{GitHub}.
An informative video showing the usage of \webprov{} is found on \href{https://youtu.be/UzwHtptkYOU}{YouTube}.

@@

% How is the information of the provenance graph saved in the Neo4j database?
The main concept of \webprov{} is the Neo4j \provnode{} and the dependency graph created from related \provnodes{} using Neo4j relationships.
A \provnode{} represents an entity or activity and, therefore, must have a classification (e.g., \SM{} or \BSM{}) which defines the types of relationships that can be formed with other nodes depending on our PROV ontology.
For example, the entity \SM{} can only be created by either the activity \BSM{} or \CSM{} (see the \nameref{sec:ResultsAndDiscussion} section and Table~\ref{tab:entitiesandactivities} for all details).
These classifications can be easily changed and extended if needed.
Additionally, \texttt{Study} nodes store information about a particular study (a study reference as well as the name of the signaling pathway it is concerned with) and group a set of \provnodes{} together.
Finally, \texttt{InformationField} nodes allow us to attach zero or more key--value pairs to a \provnode{} to store further information.
In our case, we describe which information should be entered depending on the entity type in the \nameref{sec:ResultsAndDiscussion} section.

>>>>

%3) What is the methodology being used to answer the stated research question? (81 words)
Therefore, we exploit the provenance data model, PROV-DM, of the World Wide Web Consortium and, building on previous work, continue developing a PROV ontology for simulation studies.
Based on a case study of 19 \wnt{}/\bcat{} signaling models, we identify crucial entities and activities as well as useful metadata to both capture the provenance information of individual simulation studies and relate these forming a family of models.
The approach is implemented in \href{https://github.com/SFB-ELAINE/WebProv}{\webprov{}}, a web application that allows one to insert and query provenance information.

%4) What are the results obtained? (73 words)
Our specialization of PROV-DM contains the entities \RQ{}, \A{}, \R{}, \QM{}, \SM{}, \SE{}, \SD{}, and \WD{} as well as activities that include building, calibrating, validating, and analyzing a simulation model.
We show that most \wnt{} simulation models are connected to other \wnt{} models by using (parts of) these models.
However, the overlap, especially regarding the \WD{} used for calibration or validation of the models is small.

%5) What is the meaning and importance of these results? (52 words)
Making these aspects of developing a model explicit and queryable is an important step for assessing and reusing simulation models more effectively.
Exposing this information helps to integrate a new simulation model within a family of existing ones.
Our approach may lead to the development of more robust and valid simulation models.
% TODO combine above?

%6) What are the directions for follow-up research?  (24 words)
We hope that it becomes part of a standardization effort and that modelers adopt the benefits of provenance when considering or creating simulation models.
% TODO what is "it" above?

@@

We revise a provenance ontology for simulation studies of cellular biochemical models.
Provenance information is useful for understanding the creation of a simulation model because it not only contains information about the entities and activities that have led to a simulation model, but also the relations, all of which can be visualized.
It provides additional structure as research questions, assumptions, and requirements are singled out and explicitly related along with data, qualitative models, simulation models, and simulation experiments through a small set of predefined but extensible activities.
% TODO the above sentence doesn't make sense

We have applied our concept to a family of 19 \wnt{} signaling models and implemented a web-based tool (\webprov{}) to store the provenance information of these studies.
The resulting provenance graph visualizes the story line of simulation studies and demonstrates the creation and calibration of simulation models, the successive attempts of validation and extension, and shows, beyond an individual simulation study, how the \wnt{} models are related.
% TODO what do you mean by successive attempts?
Thereby, the steps and sources that contributed to a simulation model are made explicit.

@@

A plethora of work has emerged over the last two decades to support the execution and documentation of simulation studies (e.g., modeling and simulation life cycles~\cite{Balci2012}, workflows~\cite{Ruscheinski2019}, conceptual models~\cite{Wilsdorf2020b}).
Depending on the application domain, different modeling approaches have their own documentation guidelines~\cite{Monks2018, Erdemir2012, Grimm2010}.
In the case of systems biology, the \enquote{Minimum Information Requested in the Annotation of Biochemical Models (MIRIAM)}~\cite{LeNovere2005} and the \enquote{Minimum Information About a Simulation Experiment (MIASE)}~\cite{Waltemath2011} are two community standards used for documenting simulation models and corresponding simulation experiments.
A recent perspective by Porubsky et al. (2020)~\cite{Porubsky2020} looks at all stages of a biochemical simulation study and at tools supporting their reproducibility.
When looking at an entire simulation study and at the generation process of the included simulation model, these guidelines provide some indication about what information might be useful for documenting a complete simulation study as well as for establishing relationships between different simulation models.

% Why do we have more than one model for a specific system and how can we relate these models?
This is of particular interest when several simulation models for a system under consideration exist, offering different perspectives on the system, answering different questions, or reflecting the data and information available at the time of generation.
Model repositories such as BioModels~\cite{BioModels2020, BioModels2018}, JWS Online~\cite{Snoep2004}, or the CellML Model Repository~\cite{Lloyd2008} provide different means to retrieve and use simulation models.
% BioModels\footnote{\url{https://www.ebi.ac.uk/biomodels/}}, JWS Online\footnote{\url{https://jjj.biochem.sun.ac.za/}}, the CellML Model Repository\footnote{\url{https://models.cellml.org/}}
For example, querying the BioModels database for biochemical and cellular simulation models that contain proteins such as \wnt{}, Janus kinase (Jak), or mitogen-activated protein kinase (MAPK), which are associated with corresponding signaling pathways, returns 22 simulation models for \wnt{}, for 12 simulation models for Jak and 139 simulation models for MAPK (as of January 2021).
This already shows that MAPK is an intensively studied signaling pathway.
However, there is no way to easily compare these simulation models or to examine their relationships to each other.
Tools such as BiVeS~\cite{Scharm2016a} are helpful to compare different versions of one particular simulation model, but comparing different models---even of the same system---is a difficult task because the syntax of these models (e.g., the names of the species), as well as reactions, might be completely different.
Instead of analyzing the similarities and differences in the specifications of simulation models to infer possible relationships between these simulation models, we will focus on context information, such as how a simulation model has been generated.

% How do models grow larger over time and what happens then?
Particularly, larger models are usually not built from scratch~\cite{Cvijovic2014}.
In general, simulation models are the outcome of extensive, as well as interactive, model and data generation activities. These include, in addition to executing various simulation experiments and successive model refinements, the adaptation of already existing models, for example, by composition or extension~\cite{Peng2017, Peng2016, Cvijovic2014}.
Therefore, the complexity of a model grows over time as researchers add parts to the model or refine it.
Keeping track of these generation processes is the subject of provenance.

% What does provenance mean and tell us? How and where can we store this information?
Provenance provides \enquote{information about entities, activities, and people involved in producing a piece of data or thing, which can be used to form assessments about its quality, reliability or trustworthiness}~\cite{Belhajjame2013}.
Thus, it can be applied to many fields of science, art, and technology, including biochemical and cellular simulation models.
By exploiting standardized provenance data models, such as PROV-DM, this information is presented in a structured, queryable, and graphical form~\cite{Ruscheinski2018, Ruscheinski2017}.
In addition to providing crucial information about the generation of an individual simulation model and, thus, facilitating its reuse, provenance can be applied to reveal and exploit relationships between different simulation models.
% TODO the above structure should be changed?

% What is our goal of this publication? And what is the Wnt signaling pathway?
In this publication, we will identify and structure relevant information needed for the provenance of simulation studies and elucidate how a family of simulation models can be established through relating the models to each other.
% "elucidate"?
As a case study, we will concentrate on 19 simulation studies of the \wnt{}/\bcat{} signaling pathway.
Among the different \wnt{} signaling pathways, the canonical \wnt{} or \wnt{}/\bcat{} signaling pathway is the most intensively studied one, \textit{in vitro}~\cite{MacDonald2009} as well as \textit{in silico}~\cite{Lloyd-Lewis2013}.
This pathway is considered to be one of the key pathways in development and regeneration, including cell fate, cell proliferation, cell migration and adult homeostasis~\cite{Steinhart2018, Giles2003}.
In deregulated forms, it is involved in human cancers and developmental disorders~\cite{Clevers2012, Logan2004}.

Our case study refers to the \wnt{}/\bcat{} signaling pathway only, which we call \wnt{} throughout the text.
We will present and use our web-based tool \webprov{} to store, present and query provenance information from these simulation studies.
Different queries and analyses of the family of 19 \wnt{} simulation models will then be used for finding further insights into the family of \wnt{} signaling simulation models.

@@

% General procedure of collecting provenance information
In order to gather all relevant information, the publications as well as the supporting materials---as they often contain model and experiment descriptions---were read thoroughly.
Referenced publications were checked, as well, whenever they appeared to be important for the development of the simulation model.
All information that resembled provenance entities were marked.
While reading a study, a first sketch of a possible provenance graph was made.
Afterwards, a revision of all markings helped to finalize the graph and to remove duplicate entities.
Often, authors described their simulation study chronologically, which made it easy to determine the path of its development, but sometimes, the connections of the entities had to be inferred from the context.
In general, tracing the provenance of an entire simulation study in retrospective involved some interpretation of the results presented in the publication.

@@

The tool can also be installed locally for testing and replicability purposes.
Details about its installation, as well as the code, can be found on \href{https://github.com/SFB-ELAINE/WebProv}{GitHub}.
An informative video showing the usage of \webprov{} is is also on \href{https://youtu.be/UzwHtptkYOU}{YouTube}.

@@

% How is the information of the provenance graph saved in the Neo4j database?
The main concept of \webprov{} is the Neo4j \provnode{} and the dependency graph created from related \provnodes{} using Neo4j relationships.
A \provnode{} represents an entity or activity and, therefore, must have a classification (e.g., \SM{} or \BSM{}) which defines the types of relationships that can be formed with other nodes depending on our PROV ontology.
For example, the \SM{}s can only form relationships with \BSM{}s or \CSM{}s (see the \nameref{sec:ResultsAndDiscussion} section and Table~\ref{tab:entitiesandactivities} for all details).
These classifications can be easily changed or extended if necessary.
Additionally, \texttt{Study} nodes store information about a particular study (a study reference as well as the name of the signaling pathway it is concerned with) and group a set of \provnodes{} together.
% move "a study reference as well as the name of the signaling pathway it is concerned with"?
Finally, \texttt{InformationField} nodes allow us to attach zero or more key--value pairs to a \provnode{} to store further information.
In our case, we describe which information should be entered depending on the entity type in the \nameref{sec:ResultsAndDiscussion} section.
